openarchaeoCollaboration

### 2023-01-30 analysis/paper.qmd
Add user-user graph

```{r plot-graph-repo-user}
oarch_graph_repo_user <- tbl_graph(nodes_repos_users(oarch_graph),
                                   edges_user_to_repo(oarch_graph))

@@

```{r plot-graph-user-user}
# TODO
```

>>>>

```{r plot-graph-repo-user}
oarch_graph_repo_user <- tbl_graph(nodes_repos_users(oarch_graph),
                                   edges_user_to_repo(oarch_graph),
                                   directed = FALSE)

@@

```{r plot-graph-user-user}
oarch_graph_user_user <- tbl_graph(nodes_users(oarch_graph), 
                                   edges_common_repos(oarch_graph))

oarch_graph_user_user |>
  mutate(degree = centrality_degree()) |>
  filter(degree > 0) |>
  ggraph(layout = "graphopt") +
  geom_edge_link(aes(alpha = n)) +
  geom_node_point(aes(colour = category)) +
  scale_edge_alpha(trans = "log") +
  labs(edge_alpha = "Common repositories")
```
